### 2023-07-28 paper/sec-dis-pseudodata.tex
Updating paper: remaining xFitter plots (corresponding to pseudodata in main branch on 230728), including tolerance factor T in chi2, listing T values used for PDF4LHC21 and EPPS21 cases and including remarks about 68 vs 90 CL

We consider two complementary approaches to assess the
impact of LHC neutrino data on the proton and nuclear PDFs.
%
First, the Hessian profiling\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre} of prior proton and
nuclear PDF sets, taken to be PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} and
EPPS21~\cite{Eskola:2021nhw} respectively.
%
Second, the direct inclusion 
in the NNPDF global analysis framework~\cite{NNPDF:2021uiq,NNPDF:2021njg}.
%
The profiling method applied to Hessian PDF fits is based
on minimizing a goodness-of-fit error function defined as
\begin{equation}
\chi^2 = 
\sum_{i=1}^{N_{\textrm{bin}}} 
\frac{\left(  \mathcal{O}_i^{\rm (exp)}
            + \Gamma_i^{\alpha,\textrm{pd}}
              b_\alpha^{\textrm{(pd)}}
            - \mathcal{O}_i^{\rm (th)}
            - \Gamma_i^{\beta,\textrm{th}}
              b_\beta^{(\textrm{th})}
     \right)^2
     }{ \left(\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}\rp^2 }
+ \sum_\alpha \lp b_\alpha^{(\textrm{pd})}\rp^2
+ \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, ,
\label{eq:profilingchi2}
\end{equation}
with the pseudodata 
$\mathcal{O}_i^{\rm (exp)}$ defined in  Eq.~(\ref{eq:pseudo_data_v2}).
%
The correlated uncertainties for the pseudodata and for the theoretical prediction 
are contained in the nuisance parameter vectors $b^{(\textrm{pd})}$ and $b^{(\textrm{th})}$, respectively, and the total uncorrelated uncertainty is $\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}$.

@@

The profiling studies carried out in this work are performed using version 2.2.1
of the 
{\sc\small xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}.
%
To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is available in {\sc\small xFitter}.
%
All the experimental and theoretical data files used in the analysis, including
the  {\sc\small PineAPPL}  grids, are available
from the {\sc\small xFitter} repository.
%
A tolerance factor $T = \sqrt{\Delta \chi^2}=3$ is adopted for the proton
PDF profiling, corresponding approximately to the average tolerance
used in the CT18~\cite{Hou:2019efy} and MSHT20~\cite{Bailey:2020ooq} determinations,
the two Hessian sets entering the PDF4LHC21 combination.
%
The same choice was adopted in the HL-LHC projections of~\cite{AbdulKhalek:2018rok},
and a common value is used for the Hessian profiling of EPPS21.

>>>>

We consider two complementary approaches to assess the
impact of LHC neutrino data on the proton and nuclear PDFs.
%
First, the Hessian profiling\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre} of prior proton and
nuclear PDF sets, taken to be PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} and
EPPS21~\cite{Eskola:2021nhw} respectively.
%
Second, the direct inclusion 
in the NNPDF global analysis framework~\cite{NNPDF:2021uiq,NNPDF:2021njg}.
%
The profiling method applied to Hessian PDF fits is based
on minimizing a goodness-of-fit error function defined as
\begin{equation}
\chi^2 = 
\sum_{i=1}^{N_{\textrm{bin}}} 
\frac{\left(  \mathcal{O}_i^{\rm (exp)}
            + \Gamma_i^{\alpha,\textrm{pd}}
              b_\alpha^{\textrm{(pd)}}
            - \mathcal{O}_i^{\rm (th)}
            - \Gamma_i^{\beta,\textrm{th}}
              b_\beta^{(\textrm{th})}
     \right)^2
     }{ \left(\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}\rp^2 }
+ \sum_\alpha \lp b_\alpha^{(\textrm{pd})}\rp^2
+ T^2 \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, ,
\label{eq:profilingchi2}
\end{equation}
with the pseudodata 
$\mathcal{O}_i^{\rm (exp)}$ defined in  Eq.~(\ref{eq:pseudo_data_v2}).
%
The correlated uncertainties for the pseudodata and for the theoretical prediction 
are contained in the nuisance parameter vectors $b^{(\textrm{pd})}$ and $b^{(\textrm{th})}$, respectively, with $T$ the tolerance factor, and the total uncorrelated uncertainty is $\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}$.

@@

The profiling studies carried out in this work are performed using version 2.2.1
of the 
{\sc\small xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}.
%
To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is available in {\sc\small xFitter}.
%
All the experimental and theoretical data files used in the analysis, including
the  {\sc\small PineAPPL}  grids, are available
from the {\sc\small xFitter} repository.
%%
%A tolerance factor $T = \sqrt{\Delta \chi^2}=3$ is adopted for the proton
%PDF profiling, corresponding approximately to the average tolerance
%used in the CT18~\cite{Hou:2019efy} and MSHT20~\cite{Bailey:2020ooq} determinations,
%the two Hessian sets entering the PDF4LHC21 combination.
%The same choice was adopted in the HL-LHC projections of~\cite{AbdulKhalek:2018rok},
%and a common value is used for the Hessian profiling of EPPS21.
%%
For the proton PDF profiling, a tolerance of $T^2 = 10$ is adopted, as in Ref.~\cite{PDF4LHCWorkingGroup:2022cjn}. For the Hessian profiling of EPPS21, a value of $T^2 = 33$ is used, following Ref.~\cite{Eskola:2021nhw}. Notably, the PDF uncertainties in the earlier (latter) case are given at 68\% (90\%) confidence level.
%

### 2023-07-28 paper/sec-nuclearPDFs.tex
Updating paper: remaining xFitter plots (corresponding to pseudodata in main branch on 230728), including tolerance factor T in chi2, listing T values used for PDF4LHC21 and EPPS21 cases and including remarks about 68 vs 90 CL

Fig.~\ref{fig:profiling_baseline_nuclear} displays the same comparisons
as in Fig.~\ref{fig:profiling_baseline},
now for the profiling of the EPPS21 global determination of nuclear PDFs,
specifically of the set with $A=184$ (tungsten target).
%
Also in this case we consider first the impact of the baseline LHC neutrino dataset, consisting
on the FASER$\nu$2 experiment
with statistical errors only, inclusive and charm structure functions,  and charge flavour
separation.
%
The bands indicate the 68\% CL uncertainties.

@@

\caption{Same as Fig.~\ref{fig:profiling_baseline},
now for the profiling of the EPPS21 global determination of nuclear PDFs,
specifically of the set with $A=184$ (tungsten target).

@@

The bands indicate the 68\% CL uncertainties.

@@

\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_s_ratio.pdf}

>>>>

Fig.~\ref{fig:profiling_baseline_nuclear} displays the baseline result of the profiling using the EPPS21 global determination of nuclear PDFs,
specifically of the set with $A=184$ (tungsten target).
%
Also in this case we consider first the impact of the baseline LHC neutrino dataset, consisting
on the FASER$\nu$2 experiment
with statistical errors only, inclusive and charm structure functions,  and charge flavour
separation.
%
The bands indicate the 68\% CL uncertainties.

@@

\caption{The fractional uncertainties (90\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ of the EPPS21 global determination of nuclear PDFs,
specifically of the set with $A=184$ (tungsten target), compared to the results of profiling with the FASER$\nu$2 DIS projections.

@@

@@

\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_s_ratio.pdf}

### 2023-07-28 paper/sec-protonPDFs.tex
Updating paper: remaining xFitter plots (corresponding to pseudodata in main branch on 230728), including tolerance factor T in chi2, listing T values used for PDF4LHC21 and EPPS21 cases and including remarks about 68 vs 90 CL

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{
The fractional uncertainties   (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
in PDF4LHC21 compared to the results of its profiling with the FASER$\nu$2
DIS projections.
%
In the latter case, we consider both only statistical errors and statistical and systematic
errors added in quadrature.
%
The FASER$\nu$2 dataset used here accounts for both  inclusive and charm-tagged structure functions
as well as for outgoing lepton charge-separation.
%
}
\label{fig:profiling_syst}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In the following we consider the stability of the results in Fig.~\ref{fig:profiling_baseline}
with respect to the chosen experiment and integrated luminosity, the modelling of systematic
uncertainties, being able to identify or not charm production, and being able to tell part outgoing
charged leptons from anti-leptons.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{
The fractional uncertainties   (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
in PDF4LHC21 compared to the results of its profiling with the FASER$\nu$2
DIS projections.
%
In the latter case, we consider both only statistical errors and statistical and systematic
errors added in quadrature.
%
The FASER$\nu$2 dataset used here accounts for both  inclusive and charm-tagged structure functions
as well as for outgoing lepton charge-separation.
%
}
\label{fig:profiling_syst}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In the following, we consider the results obtained using only statistical uncertainties as the baseline, 
and examine stability of these results with respect to the chosen experiment and integrated luminosity, the modelling of systematic
uncertainties, being able to identify or not charm production, and being able to tell part outgoing
charged leptons from anti-leptons.
